### 2016-07-11 Proofs.tex
Proof of Theorem1 correction1
Updated Proof of Theorem 1 as per the changed syntax and some minor corrections

\section{Proofs}
\tsnote{Jon: ignore these for now.  This is Animesh's workspace.}
\begin{theorem}\label{thm}
Fix $k, m, n > 0$ and define a hash-based filter as in section \ref{sec:hbf}, except the hash functions are defined by $h_j(x) = \left( f_{K_0}(x) + j\cdot g_{K_1}(x)\right) \bmod m$. Let $Func(m,m)$ be the set of all functions $\rho \colon \calK \times \bits^m \sends \bits^m$. Let $B_1, B_2$ be 2 adversaries attacking the PRF advantage of $F \colon \calK \times \bits^m \sends \bits^m$ and $A$ be another adversary attacking the false positive game of hash-based filters, then

\begin{equation}
\AdvFPSecHash{B}{A} = \abs{ \AdvPRF{F}{B_2} - \AdvPRF{F}{B_1}} \pm q \cdot \epsilon
\end{equation}
Note: Here, $q$ is the number of queries made to the $\QryOracle$ oracle and $\epsilon$ is the false positive error in the double hashing scheme given by Kirsch and Mitzenmacher. $\epsilon \rightarrow 0$, if $m/n \rightarrow \infty$ and/or $k \rightarrow \infty$ \cite{xxx}
\end{theorem}

\begin{proof}
The proof of the theorem will use a game playing argument as shown in Fig. \ref{fig:Game}. $\game{0}(A)$ exactly simulates $\ExpFPSecHash{B}{A}$ with hash functions $h_j(x) = \left( f_{K_0}(x) + j\cdot g_{K_1}(x)\right) \bmod m$. So,
\begin{equation}
\AdvFPSecHash{B}{A} = \Prob{\game{0}(A)=1}\label{eq:0}
\end{equation}
 $\game{1}(A)$ and $\game{2}(A)$ attack 2 different filters, $B_1$ and $B_2$, with hash functions 
\begin{eqnarray*}
h_j(x) &=& ( f_{K_0}(x) + j\cdot \rho_2(x)) \bmod m\\
h_j(x) &=& ( \rho_1(x) + j \cdot \rho_2(x)) \bmod m 
\end{eqnarray*}
Here, $\rho_1$ and $\rho_2$ are random functions sampled from $Func(m,m)$. Let adversary $B_1, B_2$ simulate $\game{1}(A)$ and $\game{2}(A)$ respectively as shown in Fig. \ref{fig:BGame1}.

\par{In a classical Bloom filter, adversary $A^{'}$ is non-adaptive, i.e., for some fixed $x \notin S$, $A^{'}$ targets the false-positive error conditioned on randomness of hash functions. But in the $\ExpFPSecHash{B}{A}$ game, $A$ is adaptive, as it can adapt its queries as well as its output based on response of $\QryOracle$ oracle. Let $A$ makes $q$ queries $x_1, x_2, ..., x_q$ to the $\QryOracle$ oracle. $\game{3}(A)$ simulates $fp-error$ game of $A^{'}$ as shown in Fig. \ref{fig:Game}.}

%\caption{Game playing argument}\label{fig:Game}
\begin{figure}[h]
\fpage{.95}{
\hpagessd{.5}{.5}
{
\underline{\game{0}(A)}\\
$K_1, K_2 \getsr \calK$\\
$S \getsr \distr{U}{n}$\\
$M \getsr \Rep^{\HashOracle(\cdot, \cdot)}(S)$\\
$x \getsr A^{\QryOracle(\cdot)}(S)$\\
if $x \not\in S \wedge \Qry^{\HashOracle(\cdot, \cdot)}(M,x)=1$ then\\
\nudge Ret 1\\
Ret 0\\\\
%
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle(\cdot, \cdot)}(M,x)$\\\\
%
\oracle{$\HashOracle(i,x)$}\\
$h_i(x) = F_{K_1}(x)+i \cdot F_{K_2}(x)$\\
Ret $h_i(x)$
}
{
\underline{\game{1}(A)}\\
$K_1 \getsr \calK$\\
$\rho \getsr Func(m,m)$\\
$S \getsr \distr{U}{n}$\\
$M \getsr \Rep^{\HashOracle(\cdot, \cdot)}(S)$\\
$x \getsr A^{\QryOracle(\cdot)}(S)$\\
if $x \not\in S \wedge \Qry^{\HashOracle(\cdot, \cdot)}(M,x)=1$ then\\
\nudge Ret 1\\
Ret 0\\\\
%
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle(\cdot, \cdot)}(M,x)$\\\\
%
\oracle{$\HashOracle(i,x)$}\\
$h_i(x) = F_{K_1}(x)+i \cdot \rho(x)$\\
Ret $h_i(x)$
}
{
\underline{\game{2}(A)}\\
$\rho_1,\rho_2 \getsr Func(m,m)$\\
$S \getsr \distr{U}{n}$\\
$M \getsr \Rep^{\HashOracle(\cdot, \cdot)}(S)$\\
$x \getsr A^{\QryOracle(\cdot)}(S)$\\
if $x \not\in S \wedge \Qry^{\HashOracle(\cdot, \cdot)}(M,x)=1$ then\\
\nudge Ret 1\\
Ret 0\\\\
%
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle(\cdot, \cdot)}(M,x)$\\\\
%
\oracle{$\HashOracle(i,x)$}\\
$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$\\
Ret $h_i(x)$
}
{
\underline{$\game{3}(A)$}\\
$t \getsr [q]$, where $[q] = {0,1, \cdots, q-1}$\\
$count = 0$ \\%count will be used to keep track of queries made to $\QryOracle$\\
$win \gets false$\\
$\rho_1,\rho_2 \getsr Func(m,m)$\\
$S \getsr \distr{U}{n}$\\
$M \getsr \Rep^{\HashOracle(\cdot, \cdot)}(S)$\\
$x \getsr A^{\QryOracle(\cdot)}(S)$\\
if $x \not\in S \wedge \Qry^{\HashOracle(\cdot, \cdot)}(M,x)=1$ then\\
$\nudge $ Ret 1\\
Ret 0\\\\
%
\oracle{$\QryOracle(x)$}\\
$count=count +1$\\
if $(count == t)$\\
$\nudge win = true$\\
$\nudge \mathrm{Ret} \nudge \Qry^{\HashOracle(\cdot, \cdot)}(M,x)$\\
else \\
$\nudge \mathrm{Ret}\nudge 0$\\\\
%
\oracle{$\HashOracle(i,x)$}\\
$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$\\
Ret $h_i(x)$
}
}
\caption{Game playing argument}\label{fig:Game}
\end{figure}

%\caption{Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
\begin{figure}[h]
\centering
\fpage{0.9}{
\hpagessl{0.5}{0.5}
{
$\experimentv{Adversary \nudge B_1^{\calO}:}$\\
$K_1 \getsr \calK $\\
$S \getsr \distr{U}{n}$\\
$M \getsr \Rep^{\HashOracle(\cdot, \cdot)}(S)$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge$ Ret $\Qry^{\HashOracle(\cdot, \cdot)}(M,x)$\\
When $A$ halts with output $x^{'}$: \\
$\nudge$if $x^{'} \not\in S \wedge \Qry^{\HashOracle(\cdot, \cdot)}(M,x^{'})=1$ then\\
$\nudge$ $\nudge$ Ret 1\\
$\nudge$ Ret 0\\\\
\oracle{$\HashOracle(i,x)$}\\
$ \mathrm{Ret} \nudge F_{K_1}(x) + i\cdot \calO(x)$\\
}
{
$\experimentv{Adversary \nudge B_2^{\calO}:}$\\
%$d \getsr \bits $\\
$\rho_2 \getsr Func(m,m)$\\
$S \getsr \distr{U}{n}$\\
$M \getsr \Rep^{\HashOracle(\cdot, \cdot)}(S)$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge$ Ret $\Qry^{\HashOracle(\cdot, \cdot)}(M,x)$\\
When $A$ halts with output $x^{'}$: \\
$\nudge$if $x^{'} \not\in S \wedge \Qry^{\HashOracle(\cdot, \cdot)}(M,x^{'})=1$ then\\
$\nudge$$\nudge$ Ret 1\\
$\nudge$Ret 0\\\\
\oracle{$\HashOracle(i,x)$}\\
%if $d=0$\\
$\mathrm{Ret} \nudge \calO(x) + i\cdot \rho_2(x)$
}
}
\caption{Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
\end{figure}

\begin{eqnarray}
\nonumber \Prob{\ExpPRF{F}{B_1} = 1} &=& .5\Prob{\ExpPRF{F}{B_1}=1|b=0} + .5\Prob{\ExpPRF{F}{B_1} = 1|b=1}\\
\nonumber (2\Prob{\ExpPRF{F}{B_1} = 1} - 1) + 1 &=& \Prob{\game{1}(A)=1} + \Prob{\game{0}(A)=1}\\
 1 + \AdvPRF{F}{B_1} &=& \Prob{\game{1}(A)=1} + \Prob{\game{0}(A)=1} \label{eq:1}\\
\nonumber& &\\
\nonumber \Prob{\ExpPRF{F}{B_2} = 1} &=& .5\Prob{\ExpPRF{F}{B_2}=1|b=0} + .5\Prob{\ExpPRF{F}{B_2} = 1|b=1}\\
\nonumber (2\Prob{\ExpPRF{F}{B_2} = 1} - 1) + 1 &=& \Prob{\game{2}(A)=1} + \Prob{\game{1}(A)=1}\\
 1 + \AdvPRF{F}{B_2} &=& \Prob{\game{2}(A)=1} + \Prob{\game{1}(A)=1}\label{eq:2}
\end{eqnarray}

Subtracting \ref{eq:1} from \ref{eq:2}, we have
\begin{eqnarray}
\abs{ \AdvPRF{F}{B_2} - \AdvPRF{F}{B_1}} &= \abs{\Prob{\game{2}(A)=1} - \Prob{\game{0}(A)=1}}\label{eq:2a}
\end{eqnarray}

@@

%\caption{Adversary $A^{'}$ simulating $\game{3}(A)$} \label{AGame3}
\begin{figure}
\centering
\fpage{0.4}{
$\experimentv{Adversary \nudge A^{{'}\HashOracle(\cdot, \cdot)}:}$\\
$t \getsr [q]$, where $[q] = {0,1, \cdots, q-1}$\\
$count = 0$\\
$\rho_1,\rho_2 \getsr Func(m,m)$\\
$S \getsr \distr{U}{n}$\\
$M \getsr \Rep^{\HashOracle(\cdot, \cdot)}(S)$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge cnt = cnt + 1$\\
$\nudge \mathrm{if} \nudge count == t$\\
$\nudge r \gets \Qry^{\HashOracle(\cdot, \cdot)}(M,x)$\\
if $r==1$\\
$\nudge$ $A$ halts with output $x$\\
$\nudge$ Ret 1\\
else\\
$\nudge$ $A$ outputs NULL\\
$\nudge$ Ret 0\\\\
%
\oracle{$\HashOracle(i,x)$}\\
$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$\\
Ret $h_i(x)$
}
\caption{Adversary $A^{'}$ simulating $\game{3}(A)$} \label{AGame3}
\end{figure}

From eqn. \ref{eq:0}, \ref{eq:2a}, \ref{eq:3} and \ref{eq:4}: \\
\begin{eqnarray}
\nonumber \abs{ \AdvPRF{F}{B_2} - \AdvPRF{F}{B_1}} &=& \abs{q \cdot \epsilon - \Prob{\ExpFPSecHash{B}{A}=1}}\\
\AdvFPSecHash{B}{A} &=& \abs{ \AdvPRF{F}{B_2} - \AdvPRF{F}{B_1}} \pm q \cdot \epsilon
\end{eqnarray}
\end{proof}

>>>>

\section{Proofs}
\tsnote{Jon: ignore these for now.  This is Animesh's workspace.}
\begin{theorem}\label{thm}
Fix $k, m, n > 0$ and define a hash-based filter as in section \ref{sec:hbf}, except the hash functions are defined by $h_j(x) =  F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$, where $F \colon \calK \times U \sends [m]$ is a PRF. Let $Func(U,[m])$ be the set of all functions $\rho \colon \calK \times U \sends [m]$. Let $B_1, B_2$ be 2 adversaries attacking the PRF advantage of $F$, and $A$ be another adversary attacking the false positive game of hash-based filters with private hash functions, then 
\begin{equation}
\AdvFPSecHash{B,t}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2} + q \cdot \epsilon
\end{equation}
Note: Here, $q$ is the number of queries made to the $\QryOracle$ oracle and $\epsilon$ is the false positive error in the double hashing scheme given by Kirsch and Mitzenmacher. $\epsilon \rightarrow 0$, if $m/n \rightarrow \infty$ and/or $k \rightarrow \infty$ \cite{xxx}
\end{theorem}

\begin{proof}
The proof of the theorem will use a game playing argument as shown in Fig. \ref{fig:Game}. $\game{0}(A)$ exactly simulates $\ExpFPSecHash{B,t}{A}$ with hash functions $h_j(x) =  F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$. So,
\begin{equation}
\AdvFPSecHash{B,t}{A} = \Prob{\game{0}(A)=1}\label{eq:0}
\end{equation}
 $\game{1}(A)$ and $\game{2}(A)$ attack 2 different filters with hash functions 
\begin{eqnarray*}
h_j(x) &=& ( F_{K_0}(x) + j\cdot \rho_2(x)) \bmod m\\
\mathrm{and,}\nudge h_j(x) &=& ( \rho_1(x) + j \cdot \rho_2(x)) \bmod m 
\end{eqnarray*}

Here, $\rho_1$ and $\rho_2$ are random functions sampled from $Func(U,[m])$. Let adversaries $B_1, B_2$ simulate $\game{1}(A)$ and $\game{2}(A)$ respectively as shown in Fig. \ref{fig:BGame1}. When $b=1$, $B_1$ and $B_2$ exactly simulate $\game{0}(A)$
and $\game{1}(A)$. While, for $b=0$, $B_1$ wins, if $\game{1}(A)$ outputs 0, and  $B_2$ wins, if $\game{2}(A)$ returns 0.

\begin{eqnarray}
\Prob{\ExpPRF{F}{B_1} = 1|b=1} &=& \Prob{\game{0}(A)=1}\label{eq:m1}\\
\Prob{\ExpPRF{F}{B_2} = 1|b=1} &=& \Prob{\game{1}(A)=1}\label{eq:m2}\\
\Prob{\ExpPRF{F}{B_1} = 1|b=0} &=& 1-\Prob{\game{1}(A)=1}\label{eq:m3}\\
\Prob{\ExpPRF{F}{B_2} = 1|b=0} &=& 1-\Prob{\game{2}(A)=1}\label{eq:m4}
\end{eqnarray}

\par{In a classical Bloom filter, adversary $A^{'}$ is non-adaptive, i.e., for some fixed $x \notin S$, $A^{'}$ targets the false-positive error conditioned on randomness of hash functions. But in the $\ExpFPSecHash{B,t}{A}$ game, $A$ is adaptive, as it can adapt its queries as well as its output based on response of $\QryOracle$ oracle. Let $A$ makes $q>t$ queries $x_1, x_2, ..., x_q$ to the $\QryOracle$ oracle. $\game{3}(A)$ simulates $fp-error$ game of $A^{'}$ as shown in Fig. \ref{fig:Game}.}

%\caption{Game playing argument}\label{fig:Game}
\begin{figure}[h]
\fpage{.95}{
\hpagessd{.5}{.5}
{
\underline{\game{0}(A)}\\
$K_1, K_2 \getsr \calK$\\
$S \getsr \distr{U}{n}$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
$\calX \getsr A^{\QryOracle}(\calS)$\\
if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,\tau,x)$\\\\
%
\oracle{$\HashOracle(x)$}\\
$h_i(x) = F_{K_1}(x)+i \cdot F_{K_2}(x)$, for $i\in[1,k]$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{\game{1}(A)}\\
$K_1 \getsr \calK$\\
$\rho \getsr Func(U,[m])$\\
$S \getsr \distr{U}{n}$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
$\calX \getsr A^{\QryOracle}(\calS)$\\
if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,\tau,x)$\\\\
%
\oracle{$\HashOracle(x)$}\\
$h_i(x) = F_{K_1}(x)+i \cdot \rho(x)$, for $i\in[1,k]$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{\game{2}(A)}\\
$\rho_1,\rho_2 \getsr Func(U,[m])$\\
$S \getsr \distr{U}{n}$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
$\calX \getsr A^{\QryOracle}(\calS)$\\
if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,\tau,x)$\\\\
%
\oracle{$\HashOracle(x)$}\\
$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$, for $i\in[1,k]$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{$\game{3}(A)$}\\
$\ell \getsr [q]$, where $[q] = {0,1, \cdots, q-1}$\\
$count = 0$ \\%count will be used to keep track of queries made to $\QryOracle$\\
$win \gets false$\\
$\rho_1,\rho_2 \getsr Func(U,[m])$\\
$S \getsr \distr{U}{n}$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
$\calX \getsr A^{\QryOracle}(\calS)$\\
if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
$count=count +1$\\
if $(count == \ell)$\\
$\nudge win = true$\\
$\nudge \mathrm{Ret} \nudge \Qry^{\HashOracle}(M,\tau,x)$\\
else \\
$\nudge \mathrm{Ret}\nudge 0$\\\\
%
\oracle{$\HashOracle(x)$}\\
$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$, for $i\in[1,k]$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
}
\caption{Game playing argument}\label{fig:Game}
\end{figure}

%\caption{Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
\begin{figure}[h]
\centering
\fpage{0.9}{
\hpagessl{0.5}{0.5}
{
$\experimentv{Adversary \nudge B_1^{\calO}:}$\\
$K_1 \getsr \calK $\\
$S \getsr \distr{U}{n}$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge$ Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
When $A$ halts with output $\calX^{'}$: \\
if $|\calX^{'}| < t$ or $\calX^{'} \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists x \in \calX^{'}$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
\oracle{$\HashOracle(x)$}\\
$ \mathrm{Ret} \nudge F_{K_1}(x) + i\cdot \calO(x)$, for $i\in[1,k]$\\
}
{
$\experimentv{Adversary \nudge B_2^{\calO}:}$\\
%$d \getsr \bits $\\
$\rho_2 \getsr Func(U,[m])$\\
$S \getsr \distr{U}{n}$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge$ Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
When $A$ halts with output $\calX^{'}$: \\
if $|\calX^{'}| < t$ or $\calX^{'} \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists x \in \calX^{'}$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
\oracle{$\HashOracle(x)$}\\
%if $d=0$\\
$\mathrm{Ret} \nudge \calO(x) + i\cdot \rho_2(x)$, for $i\in[1,k]$
}
}
\caption{Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
\end{figure}

From eqns. \ref{eq:m1}, \ref{eq:m2}, \ref{eq:m3} and \ref{eq:m4},
\begin{eqnarray}
\nonumber \Prob{\ExpPRF{F}{B_1} = 1} &=& .5\Prob{\ExpPRF{F}{B_1}=1|b=0} + .5\Prob{\ExpPRF{F}{B_1} = 1|b=1}\\
\nonumber 2\Prob{\ExpPRF{F}{B_1} = 1} &=& 1-\Prob{\game{1}(A)=1} + \Prob{\game{0}(A)=1}\\
\nonumber (2\Prob{\ExpPRF{F}{B_1} = 1} - 1)  &=& \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1}\\
 \AdvPRF{F}{B_1} &=& \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1} \label{eq:1}\\
\nonumber& &\\
\nonumber \Prob{\ExpPRF{F}{B_2} = 1} &=& .5\Prob{\ExpPRF{F}{B_2}=1|b=0} + .5\Prob{\ExpPRF{F}{B_2} = 1|b=1}\\
\nonumber 2\Prob{\ExpPRF{F}{B_2} = 1} &=& 1-\Prob{\game{2}(A)=1} + \Prob{\game{1}(A)=1}\\
\nonumber (2\Prob{\ExpPRF{F}{B_2} = 1} - 1)  &=& \Prob{\game{1}(A)=1} - \Prob{\game{2}(A)=1}\\
 \AdvPRF{F}{B_2} &=& \Prob{\game{1}(A)=1} - \Prob{\game{2}(A)=1} \label{eq:2}
\end{eqnarray}

Adding eqn. \ref{eq:1} and \ref{eq:2}, we have
\begin{equation}
\AdvPRF{F}{B_2} +\AdvPRF{F}{B_1} = \Prob{\game{0}(A)=1} - \Prob{\game{2}(A)=1}\label{eq:2a}
\end{equation}

@@

%\caption{Adversary $A^{'}$ simulating $\game{3}(A)$} \label{AGame3}
\begin{figure}
\centering
\fpage{0.4}{
$\experimentv{Adversary \nudge A^{{'}\HashOracle}:}$\\
$\ell \getsr [q]$, where $[q] = {0,1, \cdots, q-1}$\\
$count = 0$\\
$\rho_1,\rho_2 \getsr Func(U,[m])$\\
$S \getsr \distr{U}{n}$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge cnt = cnt + 1$\\
\nudge if $count == \ell$\\
$\nudge$ $\nudge r \gets \Qry^{\HashOracle}(M,\tau,x)$\\
\nudge else\\
$\nudge$ $\nudge r = 0$\\
\nudge Ret $r$\\
When $A$ halts with output $\calX^{'}$\\
\nudge if $|\calX^{'}| < t$ or $\calX^{'} \cap \calS \neq \emptyset$ then \\
\nudge\nudge Ret 0\\
\nudge if $\exists x \in \calX^{'}$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
\nudge \nudge Ret 0\\
\nudge Ret 1\\
%
\oracle{$\HashOracle(x)$}\\
$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$, for $i\in[1,k]$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
\caption{Adversary $A^{'}$ simulating $\game{3}(A)$} \label{AGame3}
\end{figure}

From eqn. \ref{eq:0}, \ref{eq:2a}, \ref{eq:3} and \ref{eq:4}: \\
\begin{eqnarray}
\nonumber \AdvFPSecHash{B,t}{A} &-& \Prob{\game{2}(A)=1} =  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}   \\
\nonumber \AdvFPSecHash{B,t}{A}  &=&  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2} + \Prob{\game{2}(A)=1}  \\
\AdvFPSecHash{B,t}{A} &\leq&  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  + q \cdot \epsilon
\end{eqnarray}
\end{proof}

\clearpage
\section{Summary of attacks(based on Bloom filter exploit) on Squid}
\acnote{For reference}\\
\heading{Crossby and Wallach: Squid Attack on hash tables} 
\begin{itemize}
\item A Squid server was ran on a stand-alone machine.
\item A file containing a list of URL's was prepared.
\item The URL requests were parsed and served by the Squid server. This completed the set-up phase.
\item Crossby and Wallach targeted hash collisions in Squid to increase the average URL load time. The authors quote ``This attack does not represent a ''smoking gun” for algorithmic complexity attacks, but it does illustrate how common network services may be sensitive to these attacks". 2 experiments were carried out to illustrate this.
\item In experiment 1, around 143K random URL's were requested to the proxy server, whereas in experiment 2, same number of carefully chosen URL's that collide with the already present URL's in the hash-table were requested. 
\item Observation: The load time of random URL's was less than the chosen URL's. It must be noted that, the authors did not use a brute-force approach to find collisions. Rather,  they proposed an efficient method to find hash-collisions. The method involves finding a set of elements that hash to the same index and using a combination of those elements to find more elements. 
\end{itemize}

\heading{Gerber et. al. : Squid attack on cache digest:}
\begin{itemize}
\item Squid servers follow a hierarchical model, and in this model the peers can exchange summary of their cache using Bloom filters(cache-digest). 
\item In the set-up phase, the authors configure 2 peer Squid servers for caching and an HTTP server which responds to all queries of the Squid servers. 
\item Peer 1's cache-digest is polluted using fake URL's. Both the peers exchange their cache-digests 
\item Client(s) of Peer 2, start making URL requests. The URL's which are not cached by the latter are searched in its neighbors cache-digest and false positives are counted.
\item Observation: There is a substantial increase in FP's due to pollution as compared to FP's without it.
\item Reason: Fake URL's increase the Hamming weight of the cache digest of peer 1 and hence increase false positives.
\end{itemize}

### 2016-07-11 intro.tex
Updated Proof of Theorem 1 as per the changed syntax and some minor corrections

\section{Introduction}
We revisit the formalization of Bloom filters~\cite{xxx} and closely related data structures as primitives with explicit security goals. Recently, Naor and Yogev~\cite{xxx} (hereafter NY) gave such a formalization, providing syntax for a generalized abstraction of Bloom filters, as well as casting the classical Bloom filter soundness condition as a security experiment admiting adaptive adversaries.  To briefly summarize, a Bloom filter is a data structure for compactly representing a set~$\mathcal{S}$ in a way that supports constant-time responses to set-membership queries. The representation of~$\mathcal{S}$ is an bit-array~$M$ of length~$m$, all initially set to~0.  To insert $x \in \mathcal{S}$ into~$M$, one computes indices $h_1(x),h_2(x),\ldots,h_k(x)$ where each $h_i \colon \mathcal{U} \to \{0,1,\ldots m-1\}$ maps from a universe~$\mathcal{U}$ (which contains $\mathcal{S}$) to indices of~$M$.  The bits at positions $h_1(x),h_2(x),\ldots,h_k(x)$ are set to 1; if a bit is already 1, due to inserting some previous element of~$\mathcal{S}$, then it is left alone.  After all elements of~$\mathcal{S}$ have been inserted, the resulting bit-array~$M$ is taken as the representation.  To test if $y \in \mathcal{S}$, one checks if \[(M[h_1(y)]=1 \wedge M[h_2(y)]=1 \wedge \cdots \wedge M[h_k(y)]=1),\] returning ``yes'' if so, and ``no'' otherwise. Bloom filters are correct, in the sense that if $y \in \mathcal{S}$, the set-membership test always returns ``yes''.  The classical soundness condition asserts that for all $\mathcal{S}$ and any $y \notin\mathcal{S}$, we have $\Prob{h_1,h_2,\ldots,h_k \getsr \mathrm{Func}(\mathcal{U},[m])\colon M[h_1(y)]=1 \wedge \cdots \wedge M[h_k(y)]=1} \leq \epsilon$ where $\epsilon$, the false-positive rate, is a parameter of the Bloom filter.  (The values of~$\epsilon,m,k$, and $|\mathcal{S}|$ are related in a well-known way.) NY recast this soundness condition as a game in which an adversary~$A$ is given~$\mathcal{S}$ and an oracle for set-membership queries, and it attempts to find a false positive. The fact that~$A$ can \emph{adapt} its queries and its output based on what it learns from the set-membership oracle (but, as we will see, not upon the hash functions) is the key definitional contribution of~NY.

>>>>

\section{Introduction}
We revisit the formalization of Bloom filters~\cite{xxx} and closely related data structures as primitives with explicit security goals. Recently, Naor and Yogev~\cite{xxx} (hereafter NY) gave such a formalization, providing syntax for a generalized abstraction of Bloom filters, as well as casting the classical Bloom filter soundness condition as a security experiment admiting adaptive adversaries.  To briefly summarize, a Bloom filter is a data structure for compactly representing a set~$\mathcal{S}$ in a way that supports constant-time responses to set-membership queries. The representation of~$\mathcal{S}$ is a bit-array~$M$ of length~$m$, all initially set to~0.  To insert $x \in \mathcal{S}$ into~$M$, one computes indices $h_1(x),h_2(x),\ldots,h_k(x)$ where each $h_i \colon \mathcal{U} \to \{0,1,\ldots m-1\}$ maps from a universe~$\mathcal{U}$ (which contains $\mathcal{S}$) to indices of~$M$.  The bits at positions $h_1(x),h_2(x),\ldots,h_k(x)$ are set to 1; if a bit is already 1, due to inserting some previous element of~$\mathcal{S}$, then it is left alone.  After all elements of~$\mathcal{S}$ have been inserted, the resulting bit-array~$M$ is taken as the representation.  To test if $y \in \mathcal{S}$, one checks if \[(M[h_1(y)]=1 \wedge M[h_2(y)]=1 \wedge \cdots \wedge M[h_k(y)]=1),\] returning ``yes'' if so, and ``no'' otherwise. Bloom filters are correct, in the sense that if $y \in \mathcal{S}$, the set-membership test always returns ``yes''.  The classical soundness condition asserts that for all $\mathcal{S}$ and any $y \notin\mathcal{S}$, we have $\Prob{h_1,h_2,\ldots,h_k \getsr \mathrm{Func}(\mathcal{U},[m])\colon M[h_1(y)]=1 \wedge \cdots \wedge M[h_k(y)]=1} \leq \epsilon$ where $\epsilon$, the false-positive error, is a parameter of the Bloom filter.  (The values of~$\epsilon,m,k$, and $|\mathcal{S}|$ are related in a well-known way.) NY recast this soundness condition as a game in which an adversary~$A$ is given~$\mathcal{S}$ and an oracle for set-membership queries, and it attempts to find one or more false positives. The fact that~$A$ can \emph{adapt} its queries and its output based on what it learns from the set-membership oracle (but, as we will see, not upon the hash functions) is the key definitional contribution of~NY.
